Preparation Giancarlo venue to CWI.

Data; 
SOHO
* magnetic field, chaotic;
** black/white indicates the direction
* X-ray emissions; (spectral line of particular atoms, four wavelentgths)
SDO: same, but more wavelengths; and already combined together (would have to be done manually from SOHO).

two frequencies + MAGNETIC.

First layers, 
convolution + batch norm;
symmetric central patch; tri-dimensional tensor; 
Mhamed used also LASCO C3; 

Part 1: semi-empirical near-Sun module that approximates the outflow at the base of the solar wind.
Part 2: a sophisticated 3D magnetohydrodynamic numerical model that simulates the resulting flow evolution on the Earth.

--------------
System CDT (Causal Dynamic Time Lag).
[WAW (What and When)]
* Artificial datasets: all good.
* Real-world data: we still miss the proper input/the important data.
** magnetic must be there
** needs a time window in the image (to extract the angular speed ? omega).
** what about x-rays emission ? Travels very fast; says something about the presence of events.

------------------
First sanity check/ visual input -wise
2010, SDO; chocolate image (aia 193 frequency).
predict the solar wind t + 3 days.

Second sanity check:
image now; image 27 days before; series of solar wind speed in the [t-27, t] period.

--------------
Giancarlo:
* wants to implement and train convolutional RBM on solar images;
* try adaptation for translation invariances with RBM models; 
* convolutional RBM is what I would do first; also, generative models; could be GAN or auto-encoders;
* experiment with standard models; 
* would be nice to understand how to generate good features; nice features; proper representation; just to compress data;

Mandar:
* could be interested to emulate the module 1 above; time series of images;  
* learning the representation and the dynamics; how evolves along time; compression very useful for further prediction;
* many time slices of images; 

Giancarlo:
* interesting; practically; treat time individually as a prediction problem; 

Mandard:
* after the compression, the prediction

Cyril:
* learn the rotation
* entire rotation period; 

Domain adaptation
* SOHO and SDO give two views of the same information; redundant ? can predict one from the other ? (green and chocolate); 






